---
title: "Ex_1_Tiffany_Scholier"
format: html
editor: visual
---

# This quarto document gives an overview of the workflow in R to:<br>
**1)** sample 100 random numbers from a log distribution with a given mean and sd<br>
**2)** calculate the mean and sd from this dataset<br>
**3)** create plots with the use of the ggplot2 R package<br>

## Load R packes
```{r}
library(ggplot2)
library(reshape2)
```

## Randomly sample 100 values from a log-normal distribution 
```{r}
values <- rlnorm(100, 5, 0.5)
mean_final <- mean(values)
sd_final <- sd(values)
```
The mean and standard deviation of this subset are `r mean_final` and `r sd_final`, respectively.

## Create plots
### Histogram with a linear scale
```{r}
ggplot(data.frame(values), aes(values)) + geom_histogram(bins = 100)
```
### Histogram with a log scale
```{r}
ggplot(data.frame(log(values)), aes(log(values))) + geom_histogram(bins = 100)
```
### Violin plot
```{r}
data <- reshape2::melt(data.frame(values), id.vars = NULL)
p <- ggplot(data, aes(x = variable, y = value)) + 
  geom_violin()
p
```

